mode speeds used in the ithim-global model

### 2020-11-21 code/trips_analysis/mode_speed_summary.Rmd
minor edits to trip distances

>>>>

### Use mean of median speeds instead of pooled medians to get default speeds.
Current work stream does not account for males and females, so we can keep that differentiation for later.  
```{r}
trip_2 %>% 
  group_by(city, mode) %>% 
  summarise(median_speed = median(speed)) %>% 
  group_by(mode) %>% 
  summarise(mean_median = mean(median_speed)) %>% 
  kable()

default_speeds <- list(
    bus=11,
    bus_driver=11,
    minibus=11,
    minibus_driver=11,
    car=14,
    taxi=9,
    pedestrian=3,
    walk_to_pt=10,
    cycle=7,
    motorcycle=14,
    truck=11,
    van=14,
    subway=16,
    rail=20,
    auto_rickshaw=9,
    shared_auto=14,
    shared_taxi=9,
    cycle_rickshaw=5
  )
